Using Blockchain to Create a Decentralised Distributed Firewall

### 2021-02-03 paper/paper.tex
Added basic blockchain functionality

\lstdefinestyle{c}{
	commentstyle=\color{comment},
	stringstyle=\color{string},
	keywordstyle=\color{keyword},
	basicstyle=\footnotesize\ttfamily,
	numbers=left,
	numberstyle=\tiny,
	numbersep=5pt,
	frame=lines,
	breaklines=true,
	prebreak=\raisebox{0ex}[0ex][0ex]{\ensuremath{\hookleftarrow}},
	showstringspaces=false,
	upquote=true,
	tabsize=2,
}
\title{Using Blockchain to Create a Decentralised Distributed Firewall}
\date{2021}
\author{Adam Bruce \\ \texttt{\href{mailto:a.bruce3@ncl.ac.uk}{a.bruce3@ncl.ac.uk}}}
\begin{document}
\maketitle

\begin{abstract}
Woah
\end{abstract}

@@

\subsection{LOL}

\begin{lstlisting}[language=c,style=c]
#include <stdio.h>
#include <string.h>
#include <stdlib.h>
#include <unistd.h>

struct _Person
{
	char name[32];
	unsigned int age;
};
typedef struct _Person Person;

Person* create_person(char* name, unsigned int age)
{
	if(strlen(name) > 31)
		return NULL;

	Person* person = (Person*)malloc(sizeof(Person));
	if(!person)
		return NULL;

	strncpy(person->name, name, strlen(name));
	person->age = age;

	return person;
}

int main(void)
{
   Person* me = create_person("Adam", 20);

   printf("Name: %s, Age: %d\n", me.name, me.age);

	free(me);

   return 0;
}
\end{lstlisting}

>>>>

\lstdefinestyle{c}{
	commentstyle=\color{comment},
	stringstyle=\color{string},
	keywordstyle=\color{keyword},
	basicstyle=\footnotesize\ttfamily,
	numbers=left,
	numberstyle=\tiny,
	numbersep=5pt,
	frame=lines,
	breaklines=true,
	prebreak=\raisebox{0ex}[0ex][0ex]{\ensuremath{\hookleftarrow}},
	showstringspaces=false,
	upquote=true,
	tabsize=2,
}

\lstdefinestyle{make}{
	commentstyle=\color{comment},
	stringstyle=\color{string},
	keywordstyle=\color{keyword},
	basicstyle=\footnotesize\ttfamily,
	numbers=left,
	numberstyle=\tiny,
	numbersep=5pt,
	frame=lines,
	breaklines=true,
	prebreak=\raisebox{0ex}[0ex][0ex]{\ensuremath{\hookleftarrow}},
	showstringspaces=false,
	upquote=true,
	tabsize=2,
}

\title{Using Blockchain to Create a Decentralised Distributed Firewall}
\date{February 2021}
\author{Adam Bruce \\ \texttt{\href{mailto:a.bruce3@ncl.ac.uk}{a.bruce3@ncl.ac.uk}}}
\begin{document}
\maketitle

\begin{abstract}
This is an abstract wow, isn't it beautiful. It will tell you all about what I did and some other interesting things.
This is an abstract wow, isn't it beautiful. It will tell you all about what I did and some other interesting things.
This is an abstract wow, isn't it beautiful. It will tell you all about what I did and some other interesting things.
This is an abstract wow, isn't it beautiful. It will tell you all about what I did and some other interesting things.
This is an abstract wow, isn't it beautiful. It will tell you all about what I did and some other interesting things.
This is an abstract wow, isn't it beautiful. It will tell you all about what I did and some other interesting things.
This is an abstract wow, isn't it beautiful. It will tell you all about what I did and some other interesting things.
This is an abstract wow, isn't it beautiful. It will tell you all about what I did and some other interesting things.
This is an abstract wow, isn't it beautiful. It will tell you all about what I did and some other interesting things.
\end{abstract}

@@

\subsection{LOL}
socket.h
\lstinputlisting[language={[ANSI]c},style=c]{../src/main.c}

Makefile
\lstinputlisting[language=make,style=make]{../src/Makefile}
